Playfair and the \"Flatten the Curve\" Graphic

### 2022-02-19 _posts/2022-02-19-playfair-and-the-flatten-the-curve-graphic/playfair-and-the-flatten-the-curve-graphic.Rmd
edits
build

One of the early tidbits from [Edward Tufte](https://www.edwardtufte.com)'s "[The Visual Display of Quantitative Information](https://www.edwardtufte.com/tufte/books_vdqi) is this quote from Scottish political economist William Playfair's 1786 book "The Commercial and Political Atlas":

@@

This is even more effective: the text and colors are bold and easy to read, the axis text is simplified, there are only three elements of text in the graph (each only three words), and a third item has been added: a horizontal line indicating the healthcare system's capacity. This is about as simple and direct as it's possible to make this information. It communicated a complex problem in a way that could be instantly understood, with minimal reading, by almost anyone regardless of education levels. It may have saved millions of lives, by being shared around the world and absorbed into the collective human understanding of what needed to happen to make the pandemic as manageable as possible.

>>>>

One of the early tidbits from [Edward Tufte](https://www.edwardtufte.com)'s "[The Visual Display of Quantitative Information](https://www.edwardtufte.com/tufte/books_vdqi)" is this quote from Scottish political economist William Playfair's 1786 book "The Commercial and Political Atlas":

@@

This is even more effective: the text and colors are bold and easy to read, the axis text is simplified, there are only three elements of text in the graph (each only three words), and a third item has been added: a horizontal line indicating the healthcare system's capacity. This is about as simple and direct as it's possible to make this information. It communicated a complex problem in a way that could be instantly understood, by almost anyone, regardless of education levels. It may have saved millions of lives, by being shared around the world and absorbed into the collective human understanding of what needed to happen to make the pandemic as manageable as possible.
